### 2020-01-05 cv_models.tex
updated CV models

pNorm and ResNet
pNorm and ResNet (ImageNet1K all models)
pNorm and DenseNet

>>>>

    \subfigure[ ResNet ]{
        \includegraphics[width=4.2cm]{img/resnet-accuracy.png}
        \label{fig:resnet-accuracy}
    }
    \qquad
    \subfigure[ ResNet-1K ]{
        \includegraphics[width=4.5cm]{img/resnet1k-accuracy.png}
        \label{fig:resnet1k-accuracy}
    }
    \qquad
    \subfigure[ DenseNet ]{
        \includegraphics[width=4.4cm]{img/densenet-accuracy.png}
        \label{fig:densenet-accuracy}
    }
    \caption{$\alpha$-Norm vs reported Top1 Error for  ResNet, ResNet-1K, and DenseNet models}
    \label{fig:cv2-accuracy}
\end{figure}
